

--
title: "Explore-WineReviews-BEN"
author: "Ben Chapman"
date: 2020-08-04
output:
  github_document:
    toc: true
---

*Purpose*: To create an effective visualization, we need to keep our *purpose* firmly in mind. There are many different ways to visualize data, and the only way we can judge efficacy is with respect to our purpose.

In this challenge you'll visualize the same data in two different ways, aimed at two different purposes.


```{r setup}
library(tidyverse)
library(ggrepel)

```


```{r load}

filename <- "winemag-data-130k-v2.csv"

## Load the data
df_wine <- read_csv(filename)
```
```{r 1}
df_wine %>% 
  ggplot()+
  geom_point(aes(x = price, y = points))
```

```{r 2}

df_wine %>% 
  ggplot()+
  geom_histogram(aes( x = points, binwidth = 5, edge =90))+
  ggtitle("Histogram of Points")

df_wine %>% 
  ggplot()+
  geom_density(aes( x = price))+
  ggtitle("Density of Price")+
  scale_x_log10()


```
```{r}
df_wine %>% 
  filter(country == "Portugal" | country == "US" | country == "France" | country == "Italy" | country == "Austria") %>% 
  ggplot()+
  geom_density(aes( x = price, color = country))+
    ggtitle("Density of Price")+
  scale_x_log10()

  
```

```{r 3}

summary(df_wine)
glimpse(df_wine)
```
```{r 4}


df_wineries <- df_wine %>% 
group_by(winery) %>% 
   summarize(avgprice = median(price, na.rm = TRUE), "avgpoints" = mean(points, na.rm = TRUE), "n" = n(), stdevpoints = sd(points, na.rm = TRUE) ) %>% 
  filter(n>20) %>% 
  arrange(desc(n))
  
df_wineries %>% 
  filter(n>115| (n>25 & avgpoints > 93) | (n > 40 & avgprice < 10)) %>%
  ggplot(aes(x = avgpoints,y = avgprice))+
  geom_point(data = df_wineries, alpha = .2)+
  geom_point( mapping = aes(size = n, color = stdevpoints), alpha = .9)+
    scale_color_gradient(low = "green", high = "black")+
  scale_y_log10()+
   scale_size(range = c(1,8), name = "Reviews")+
  geom_label_repel(aes(label = winery))+
  ggtitle("Wine Grouped By Wineries")
```
```{r 5}
df_wine %>% 
group_by(country) %>% 
  summarize(avgprice = median(price, na.rm = TRUE), "avgpoints" = mean(points, na.rm = TRUE), "n" = n()) %>% 
  filter(n>30) %>% 
  ggplot(aes(x = avgpoints,y = avgprice))+
  geom_point(aes(size = n, alpha = .5))+
  scale_size(range = c(1,24), name = "Reviews")+
  geom_label_repel(aes(label = country), size = 2)+
  ggtitle("Wine Grouped By Country")

```
```{r 6}
df_wine %>% 
group_by(variety) %>% 
  summarize("avgprice" = median(price, na.rm = TRUE), "avgpoints" = mean(points, na.rm = TRUE), "n" = n())  %>% 
  filter(n >1200) %>% 
arrange(desc(n)) %>% 
  ggplot(aes(x = avgpoints,y = avgprice))+
  geom_point(aes(size = n, alpha = .5))+
  scale_size(range = c(1,24), name = "Reviews")+
  geom_label_repel(aes(label = variety), size = 2)+
  ggtitle("Wine Grouped By Variety")
```
```{r 7}
provinces800 <- df_wine %>% 
group_by(province) %>% 
  summarize("avgprice" = median(price, na.rm = TRUE), "avgpoints" = mean(points, na.rm = TRUE), "n" = n())  %>% 
  filter(n >1000 | (avgpoints > 90 & n>60)) %>% 
arrange(desc(n))


provinces80 <- df_wine %>% 
group_by(province) %>% 
  summarize("avgprice" = mean(price, na.rm = TRUE), "avgpoints" = mean(points, na.rm = TRUE), "n" = n())  %>% 
  filter(n >60) %>% 
arrange(desc(n))

 ggplot(data = provinces80, mapping = aes(x = avgpoints,y = avgprice))+
  geom_point(aes(size = n, alpha = .5))+
  scale_size(range = c(1,24), name = "Reviews")+
  geom_label_repel(data = provinces800, mapping = aes(label = province), size = 2)+
   ggtitle("Wine Grouped By Province")
 
```


```{r 8}
df_wine %>% 
group_by(title) %>% 
  summarize("avgprice" = median(price, na.rm = TRUE), "avgpoints" = mean(points, na.rm = TRUE), "n" = n())  %>% 
  filter(n >2) %>% 
arrange(desc(n)) %>% 
   ggplot(aes(x = avgpoints,y = avgprice))+
  geom_point(aes(size = n, alpha = .5))+
  scale_size(range = c(1,4), name = "Reviews")+
  scale_y_log10()+
  geom_smooth(se = FALSE)+
  ggtitle("Wines with 3+ Reviews")

 
```

```

